### 2015-08-13 abstract.tex
updates

This project explores the use of application level knowledge to optimize the
times to insight across a workload of multiple applications in a multi-user
environment with shared storage and network resources. The basis for this
work is the notion of selectable data quality to explore the tradeoffs
between accuracy of results, resource requirements, and time to insight on
systems with shared, oversubscribed computational and storage resources. 
In the last several years extreme scale computational science was conducted
using dedicated computational resources, with shared resources, such as
network and storage, being overprovisioned. This resulted in little to no
impact from resource contention. The increased scale of recent, and incoming
future systems, has placed a greater emphasis on mitigating contention.

Our thesis is that by adding application level knowledge
about data to guide storage system behaviors, we will obtain substantial benefits
in the organization, storage, and access to extreme scale data resulting in
improved productivity for computational science. We will demonstrate novel
techniques to facilitate efficient and effective data placement onto
multiple storage tiers and enable application-guided data reductions and
transformations to address capacity and bandwidth bottlenecks. Our goal is
to address the associated data management challenges in the context of
current and emerging storage landscapes and expedite insights into mission
critical scientific processes.

>>>>

This project explores the use of application level knowledge to optimize the
times to insight across a workload of multiple applications in a multi-user
environment with shared storage and network resources. The basis for this
work is the notion of selectable data quality to explore the tradeoffs
between accuracy of results, resource requirements, and time to insight on
systems with shared, oversubscribed computational and storage resources.

Our thesis is that by adding application level knowledge about data to guide
storage system behaviors, we will obtain substantial benefits in the
organization, storage, and access to extreme scale data resulting in
improved productivity for computational science. We will demonstrate novel
techniques to facilitate efficient data placement onto multiple storage
tiers, and enable application-guided data reductions to address capacity,
bandwidth, and latency. Our goal is to address the associated data management
challenges in the context of current and emerging storage landscapes and
expedite insights into mission critical scientific processes.
